### 2014-12-03 writing/F'14 paper/intro.tex
Faster testing; test data MacroF1

Supervised recursive neural network models (RNNs) for sentence meaning
have been successful in an array of sophisticated language tasks,
including sentiment analysis \cite{socher2011semi,socher2013acl1},
image description \cite{sochergrounded}, and paraphrase detection
\cite{Socher-etal:2011:Paraphrase}. These results are encouraging for
the ability of these models to learn compositional semantic grammars,
but it remains an open question whether they can achieve the same
results as grammars based in logical forms
\cite{Warren:Pereira:1982,Zelle:Mooney:1996,ZetCol:2005,LiangJordan:2013}
when it comes to the core semantic concepts of quantification,
entailment, and contradiction needed to identify the relationships
between sentences like \ii{every animal walks}, \ii{every turtle
  moves}, and \ii{most reptiles don't move}.

To date, experimental investigations of these concepts using
distributed representations have been largely confined to short
phrases
\cite{Mitchell:Lapata:2010,Grefenstette-etal:2011,baroni2012entailment}.
However, for robust natural language understanding, it is essential to
model these phenomena in their full generality on complex linguistic
structures. Other recent work
\cite{grefenstette2013towards,rocktaschellow} has developed rich
frameworks for computing the meanings of complex fragments of natural
language compositionally from vector or tensor representations, but
these approaches have not yet attempted to learn their
highly structured representations from data using existing applied
machine learning models.

>>>>

Supervised recursive neural network models (RNNs) for sentence meaning
have been successful in an array of sophisticated language tasks,
including sentiment analysis \cite{socher2011semi,socher2013acl1},
image description \cite{sochergrounded}, and paraphrase detection
\cite{Socher-etal:2011:Paraphrase}. These results are encouraging for
the ability of these models to learn compositional semantic grammars.
However, it remains an open question whether they can achieve the
high-fidelity distributed representations of recent algebraic
approaches \cite{ClarkCoeckeSadrzadeh2011,grefenstette2013towards,rocktaschellow},
and whether they can match the performance of grammars based in logical forms
\cite{Warren:Pereira:1982,Zelle:Mooney:1996,ZetCol:2005,LiangJordan:2013}
when it comes to the core semantic concepts of quantification,
entailment, and contradiction needed to identify the relationships
between sentences like \ii{every animal walks}, \ii{every turtle
 moves}, and \ii{most reptiles don't move}.

To date, experimental investigations of these concepts using
distributed representations have been largely confined to short
phrases \cite{Mitchell:Lapata:2010,Grefenstette-etal:2011,baroni2012entailment}.
However, for robust natural language understanding, it is essential to
model these phenomena in their full generality on complex linguistic
structures. Recent work on the algebraic approach of
\newcite{ClarkCoeckeSadrzadeh2011} has yielded rich frameworks 
for computing the meanings of complex fragments of natural
language compositionally from vector or tensor representations, but
how to learn these representations entirely from data in a typical
machine learning setting remains an open question.

### 2014-12-03 writing/F'14 paper/join.tex
Faster testing; test data MacroF1

\begin{table}[tp]
  \centering \small
  \begin{tabular}{ l r@{ \ }r r@{ \ }r r@{ \ }r }
    \toprule
    ~&\multicolumn{2}{c}{$\natind$ only} & \multicolumn{2}{c}{??d RNN}  & \multicolumn{2}{c}{??d RNTN}\\
    \midrule
    Test &52.0 &(10.3) &	95...&(-)& \textbf{96.8...} & \textbf{(-)}\\
    Train &53.8 &(10.5)    & -&(-)& \textbf{-} & \textbf{(-)}\\

    \bottomrule
  \end{tabular}
  \caption{\mynote{Performance on the semantic relation experiments.} These results and all other results on artificial data are reported as mean accuracy scores over five runs followed by mean macroaveraged F1 scores in parentheses.}
  \label{joinresultstable}
\end{table}

@@

\paragraph{Results} 
Table \ref{joinresultstable} shows the results, which are straightforward 
to interpret. Both models are able to accurately encode the relations 
between the terms in the geometric relations between their vectors, 
and is able to then use that information to recover relations that 
are not overtly included in the training data.

>>>>

@@

\begin{table}[tp]
  \centering \small
  \begin{tabular}{ l r@{ \ }r r@{ \ }r r@{ \ }r }
    \toprule
    ~&\multicolumn{2}{c}{$\natind$ only} & \multicolumn{2}{c}{15d RNN}  & \multicolumn{2}{c}{15d RNTN}\\
    \midrule
    Test &52.0 &(10.3) &	94.0&(87.0)& \textbf{99.6} & \textbf{(95.5)}\\
    Train &53.8 &(10.5)    & 99.8&	(99.0) & \textbf{100} & \textbf{(100)}\\

    \bottomrule
  \end{tabular}
  \caption{Performance on the semantic relation experiments. These results and all other results on artificial data are reported as mean accuracy scores over five runs followed by mean macroaveraged F1 scores in parentheses.}
  \label{joinresultstable}
\end{table}

\paragraph{Results} 
Table \ref{joinresultstable} shows the results, which are straightforward 
to interpret. The RNTN is able to accurately encode the relations 
between the terms in the geometric relations between their vectors, 
and is able to then use that information to recover relations that 
are not overtly included in the training data. The RNN, in contrast, was not able to learn
to do this well in this setting.

### 2014-12-03 writing/F'14 paper/quantifiers.tex
Faster testing; test data MacroF1

\begin{table}[tp]
  \centering \small
  \begin{tabular}{ l r@{ \ }r r@{ \ }r r@{ \ }r }
    \toprule
    ~&\multicolumn{2}{c}{$\natind$ only} & \multicolumn{2}{c}{25d RNN}  & \multicolumn{2}{c}{25d RNTN}\\
    \midrule
    Test & 35.4 &(7.5) &	99.1&(99.2)& \textbf{99.5} & \textbf{(99.3)}\\
    Train & 35.4 &(7.5) &	100&		(100)&	100&	(100)\\	
    \bottomrule
  \end{tabular}
  \caption{\mynote{Performance on the quantifier experiments, given as \% correct and macroaveraged F1.}}
  \label{qresultstable}
\end{table} 
%
% do not allow a blank line --- adds too much space
%
\paragraph{Results} The results, reported in Figure \ref{qresultstable}, show that both models are able to learn to generalize the underlying logic well.

>>>>

\begin{table}[tp]
  \centering \small
  \begin{tabular}{ l r@{ \ }r r@{ \ }r r@{ \ }r }
    \toprule
    ~&\multicolumn{2}{c}{$\natind$ only} & \multicolumn{2}{c}{25d RNN}  & \multicolumn{2}{c}{25d RNTN}\\
    \midrule
    Test & 35.4 &(7.5) &	99.1&(99.2)& \textbf{99.5} & \textbf{(99.3)}\\
    Train & 35.4 &(7.5) &	100&		(100)&	100&	(100)\\	
    \bottomrule
  \end{tabular}
  \caption{Performance on the quantifier experiments, given as \% correct and macroaveraged F1.}
  \label{qresultstable}
\end{table} 
%
% do not allow a blank line --- adds too much space
%
\paragraph{Results} The results, reported in Figure \ref{qresultstable}, show that both models are able to learn to generalize the underlying logic well. We did not observe any consistent pattern in the few errors made by either model, and errors did not tend to be consistent across runs of the experiment.
